Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-15 ms.tex
more introduction

\begin{abstract}
We present full-sky maps of dust optical depth and temperature derived from 
the \cite{FDS99} two-component dust emission model fitted to \PLANCK~217, 353, 
545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the optical 
depth and temperature maps have angular resolution of $6.1'$. Such maps serve 
as an important alternative to and comparison for other dust 
emission models, especially the single modified blackbody model in which 
$\beta$ and $T$ both vary spatially. We also expect the derived optical 
depth to provide valuable cross-checks for other dust-column related data 
products, specifically the \cite{SFD} map, which assumed 
$\beta = 2$ single-component dust emission and included a temperature map of 
inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
best-fit two-component spectral energy distributions to those of the 
\cite{planckdust} single-component parametrization.
%mention the enhanced temperature resolution relative to SFD
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

@@

FDS99 used FIRAS to make a globally best-fit model of dust emission 
appropriate over a very broad range of frequencies. They showed that a 
model consisting of a single modified blackbody with power law index $\beta$ 
could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
a spectrum consisting of two modified black bodies, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
silicates and carbonaceous grains.

@@

\section{Data}

All \PLANCK~data products utilized throughout this work are drawn from the 
\PLANCK~2013 data release \citep{planck2013}. Specifically, we have made use 
of the the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps. We use the 
versions of these maps which have been corrected for zodiacal light 
\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}.

@@

\section{Pre-processing}

@@

\section{Dust Emission Model}
\label{sec:modeling}
Our model is that of FDS99, which consists of two populations of dust 
grains emitting as modified blackbodies, but with different temperatures
and different emissivity power law indices $\beta$. The shape of this spectrum 
is given by:

@@

\subsection{Fitting Methodology}

\section{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into independent pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization with nside=2048
\citep{healpix}. This is convenient because the Planck maps are provided in 
this format and this pixelization adequately samples the $6.1'$ resolution maps
under consideration. We reiterate that each pixel is fit independently of 
neighboring pixels.

\section{Markov Chains}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determinesthe shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $T_2$ and $\tilde{I}_{545}$. For each pixel, we 
are sampling the posterior given by:

@@

\section{Results}

@@

\subsubsection{Omitting 217 GHz}
The \cite{planckdust} result used only XX, YY, ZZ, 3000 GHz. When we 
repeat our analysis ignoring 217 GHz, so that we are using the same
set of frequencies, we find that no major changes arise. This actually
should be done/investigated though.

\section{Conclusion}

>>>>

\begin{abstract}
We present full-sky maps of dust optical depth and temperature derived from 
the \cite{FDS99} two-component dust emission model fitted to \PLANCK~217, 353, 
545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the optical 
depth and temperature maps have angular resolution of $6.1'$. Such maps serve 
as an important alternative to and comparison for other dust 
emission models, especially the single modified blackbody (MBB) model in which 
$\beta$ and $T$ both vary spatially. We also expect the derived optical 
depth to provide valuable cross-checks for other dust-column related data 
products, specifically the \cite{SFD} map, which assumed 
$\beta = 2$ single-component dust emission and included a temperature map of 
inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
best-fit two-component spectral energy distributions to those of the 
\cite{planckdust} single-component parametrization.
%mention the enhanced temperature resolution relative to SFD
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

@@

FDS99 used FIRAS to make a globally best-fit model of dust emission 
appropriate over a very broad range of frequencies. They showed that a 
model consisting of a single MBB with power law index $\beta$ 
could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
a spectrum consisting of two MBBs, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
silicates and carbonaceous grains.

\cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum.

In $\S$\ref{sec:data} we discuss the data used in throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
dust emission model we fit to the \PLANCK and \IRAS~data. In 
$S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method 
we use to estimate the parameters of our model. In $\S$\ref{sec:results} we 
present the full-sky maps of dust temperature and optical depth we have 
obtained, and conclude and $\S$\ref{sec:conclusion}

@@

\section{Data}
\label{sec:data}
All \PLANCK~data products utilized throughout this work are drawn from the 
\PLANCK~2013 data release \citep{planck2013}. Specifically, we have made use 
of the the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps. We use the 
versions of these maps which have been corrected for zodiacal light 
\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}.

@@

\section{Pre-processing}
\label{sec:prepro}

@@

\section{Dust Emission Model}
\label{sec:modeling}
Our model is that of FDS99, which consists of two populations of dust 
grains emitting as MBBs, but with different temperatures
and different emissivity power law indices $\beta$. The shape of this spectrum 
is given by:

@@

\section{Fitting Procedure}
\label{sec:fitting}

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into independent pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization with nside=2048
\citep{healpix}. This is convenient because the Planck maps are provided in 
this format and this pixelization adequately samples the $6.1'$ resolution maps
under consideration. We reiterate that each pixel is fit independently of 
neighboring pixels.

\subsection{Markov Chains}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determinesthe shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $T_2$ and $\tilde{I}_{545}$. For each pixel, we 
are sampling the posterior given by:

@@

\section{Results}
\label{sec:results}

@@

\subsubsection{Omitting 217 GHz}
The \cite{planckdust} result used only 353, 545, 857, and 3000 GHz. When we 
repeat our analysis ignoring 217 GHz, so that we are using the same
set of frequencies, we find that no major changes arise. This actually
should be done/investigated though.

\section{Conclusion}
\label{sec:conclusion}
